**Title**

### 2018-08-15 manuscript_draft.Rmd
for different conversion factors

####Microbial enzyme models (Fig. 1c)
In microbial enzyme models, microbial biomass produce extracellular enzymes. The way the carbon is partitioned between $C_{MB}$, $CO_{2}$ and $C_{Enz}$ can follow different mechanisms.

>>>>

####Microbial enzyme models (Fig. 1c)
In microbial enzyme models, microbial biomass produce extracellular enzymes. The way the carbon is partitioned between $C_{MB}$, $CO_{2}$ and $C_{Enz}$ can follow different rules.

* Classical microbial enzyme model (MEM)

Microbial enzyme model presented by Allison et al. [-@Allison2010] assumes that extracellular enzymes are produced constitutively by the rate ($r_{Enz}$), which is proportional to biomass:

[5] $~~~~~~~~~~enzyme~production~=~r_{Enz}~\times~C_{MB}$.

When extracellular enzymes are produced, microbial biomass is loosing carbon. Therefore, the mass balance equation for microbial biomass is:

[6] $~~~~~~~~~~\frac{dC_{MB}}{dt}~=~uptake~\times~CUE~-~death~-~enzyme~production$.
